Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
finalize paper for submission

#### Questionable Quantification of Reasons for Strip Search

While these findings point towards a positive correlation between police strip search being racially inclined and gendered, particularly towards the black and female population of Toronto, it's worth noting how the data has decontextualized the reasons the police account for each strip search. Specifically, each reason-- including "Injury", "Weapons", "Escape" and "Possess Evidence"--is quantified as a single, equal unit for each arrest, without other further details on the severity scale of the reason itself. This can very much seclude the fact that some arrests--even those having the same reason--are more necessary to be strip searched than others, thus skewing the nature of this paper's analysis. Moreover, referring back to @tbl-reasons-strip-search, the more number of reasons to account for a strip search doesn't necessarily mean that a person is bound to be strip searched. The number of reasons the dataset attributes to each strip search--as provided by Toronto Police Service [@torontoPolice]--can be purely projected based on the police in power's racial preconceptions or gender biases. This means that the reasons for each strip search has might be purely intuitive and subjective.

#### Problematic Categorization of Data and Identities

>>>>

#### Quantification of Reasons for Strip Search

While these findings point towards a positive correlation between police strip search being racially inclined and gendered, particularly towards the black and female population of Toronto, it's worth noting how the data has decontextualized the reasons the police account for each strip search. Specifically, each reason-- including "Injury", "Weapons", "Escape" and "Possess Evidence"--is quantified as a single, equal unit for each arrest, without other further details on the severity scale of the reason itself. This can very much seclude the fact that some arrests--even those having the same reason--are more necessary to be strip searched than others, thus skewing the nature of this paper's analysis. Moreover, referring back to @tbl-reasons-strip-search, more reasons to account for a strip search doesn't necessarily mean that a person is bound to be strip searched. The number of reasons the dataset attributes to each strip search--as provided by Toronto Police Service [@torontoPolice]--can be purely projected based on the police in power's racial preconceptions or gender biases. This means that the way the reasons are flagged out for each strip search has might be personally motivated.

#### Categorization of Data and Identities
